A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-12-21 papers/water-SAFT/paper.tex

\subsection{Ideal gas functional}
The first term is the ideal gas free energy functional, which is
purely local:
\begin{equation}\label{idealgas}
  F_{id}[n] = k_B T \int n(\xx)\left( \ln{\frac{n(\xx)}{{l_Q}^3}} - 1\right) d\xx,
\end{equation}
where n(\xx) is the density of water molecules and $l_Q$ is the
thermal wavelength
\begin{equation}\label{quantumconcentration}
 l_Q =\left(\frac{mk_BT}{2\pi\hbar^2}\right)^{1/2}.
\end{equation}
The ideal gas free energy functional on its own satisfies the contact
value theorem and its limiting case of small solutes (Equations
\ref{eq:contact} and \ref{contactvaluethm}). These properties are
retained by our total functional, since all the remaining terms are
purely nonlocal.

>>>>

\subsection{Ideal gas functional}
The first term is the ideal gas free energy functional, which is
purely local:
\begin{equation}\label{idealgas}
  F_{id}[n] = k_B T \int n(\xx)\left( \ln({n(\xx){\Lambda}^3}) - 1\right) d\xx,
\end{equation}
where n(\xx) is the density of water molecules and $\Lambda$ is the
thermal wavelength
%\begin{equation}\label{quantumconcentration}
$ \Lambda = \left(\frac{2\pi\hbar^2}{mk_BT}\right )^{1/2}$.
%\end{equation}
The ideal gas free energy functional on its own satisfies the contact
value theorem and its limiting case of small solutes (Equations
\ref{eq:contact} and \ref{contactvaluethm}). These properties are
retained by our total functional, since all the remaining terms are
purely nonlocal.
